---
title: "Project proposal"
author: "Team name"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```

## 1. Introduction

After initially discussing what route we wanted to go down with our project, scanning through many different websites such as Kaggle, the UK Gov data and the Harvard dataverse, we eventually stumbled upon a very cool dataset about Summer Olympic medal winners between the years of 1976 to 2008. The dataset has 11 variables, ranging from type of sport, type of medal won, country of athlete and many more. Our plan of action will involve breaking down the data into countries and eventually breaking it down into continents and which continents excel at which sports specifically.

## 2. Data
```{r}
head(Summer_Olympics)
```
## 3. Data analysis plan

An idea that we have is to possibly analyze each region then facet it by sport and fill by the medal colors. If we come into trouble with being able to see the graph, we can do the top ten sports, so it is easier to analyze the data. We have discussed and if it comes down to the top ten, we will pick as a group. We came to this conclusion because each region will have different sports that they like to stream during the Olympics.  Our main goal is to see what regions excel at different sports. The region variable of our data, we are going to do by continents, but we know that Antarctica will not have any data, so technically there will be only six graphs. 
	We are going into it with assumptions such as North America will be the best at sports like Basketball, Africa will tend to be better at running, and Asia will be better at diving and ping pong. In general we know there are stand out countries such as Kenya in distance running or the USA in basketball, but it will also be interesting to look at regions as a whole, not just individual countries. We will be able to see this after grouping by continent and creating a graph that differentiates between which medals were won in which sport. We could also buttress these graphs with something like correlation statistics, we will see what works best for the data when we start manipulating it. 


