---
title: "Project proposal"
author: "Team name"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(readr)
```

## 1. Introduction

Research Question: Which regions are the best in which specific sport?
After initially discussing what route we wanted to go down with our project, scanning through many different websites such as Kaggle, the UK Gov data and the Harvard dataverse, we eventually stumbled upon a very cool dataset about Summer Olympic medal winners between the years of 1976 to 2008. The dataset has 11 variables, ranging from type of sport, type of medal won, country of athlete and many more. Our plan of action will involve breaking down the data into countries and eventually breaking it down into continents and which continents excel at which sports specifically.

How are we going to analyze the data? 
An idea that we have is to possibly analyze each region then facet it by sport and fill by the medal colors. If we come into trouble with being able to see the graph, we can do the top ten sports, so it is easier to analyze the data. We have discussed and if it comes down to the top ten, we will pick as a group. We came to this conclusion because each region will have different sports that they like to stream during the Olympics.  Our main goal is to see what regions excel at different sports. The region variable of our data, we are going to do by continents, but we know that Antarctica will not have any data, so technically there will be only six graphs. 
	We are going into it with assumptions such as North America will be the best at sports like Basketball, Africa will tend to be better at running, and Asia will be better at diving and ping pong. In general we know there are stand out countries such as Kenya in distance running or the USA in basketball, but it will also be interesting to look at regions as a whole, not just individual countries. We will be able to see this after grouping by continent and creating a graph that differentiates between which medals were won in which sport. We could also buttress these graphs with something like correlation statistics, we will see what works best for the data when we start manipulating it.



## 2. Data
Data: https://www.kaggle.com/divyansh22/summer-olympics-medals
```{r load-data, echo = FALSE}
Summer_Olympics <- read_csv("data/Summer-Olympic-medals-1976-to-2008.csv")
glimpse(Summer_Olympics)
```

After initially discussing what route we wanted to go down with our project, scanning through many different websites such as Kaggle, the UK Gov data and the Harvard dataverse, we eventually stumbled upon a very cool dataset about Summer Olympic medal winners between the years of 1976 to 2008. The dataset has 11 variables, ranging from type of sport, type of medal won, country of athlete and many more. Our plan of action will involve breaking down the data into countries and eventually breaking it down into continents and which continents excel at which sports specifically.

## 2. Data
```{r}
head(Summer_Olympics)
```
## 3. Data analysis plan
The variables we will be using are medals, region (which we will create), country and possibly a few more. We are looking to see which regions of the world are the best at which sports, and how they differ around the world. We are looking to use summary statistics as well as geom_bar and geom_point to show how certain regions excel at certain sports. We are excited to get to work on this project and see how the project plays out and what findings we have.

An idea that we have is to possibly analyze each region then facet it by sport and fill by the medal colors. If we come into trouble with being able to see the graph, we can do the top ten sports, so it is easier to analyze the data. We have discussed and if it comes down to the top ten, we will pick as a group. We came to this conclusion because each region will have different sports that they like to stream during the Olympics.  Our main goal is to see what regions excel at different sports. The region variable of our data, we are going to do by continents, but we know that Antarctica will not have any data, so technically there will be only six graphs. 
	We are going into it with assumptions such as North America will be the best at sports like Basketball, Africa will tend to be better at running, and Asia will be better at diving and ping pong. In general we know there are stand out countries such as Kenya in distance running or the USA in basketball, but it will also be interesting to look at regions as a whole, not just individual countries. We will be able to see this after grouping by continent and creating a graph that differentiates between which medals were won in which sport. We could also buttress these graphs with something like correlation statistics. We plan to use things like mean medals won per event by country, find correlation statistics between winningness and region, and use things like mode to find the frequency of repeated results. We will also make a tier system of Gold medals being worth 3, Silver worth 2, and Bronze worth 1, so we can create a gradient for performance among medal winners. By assigning a number to all of these medals, we can use things like mean to evaluate the success of a region in a sport and we can make graphs to represent these statistics. A country with a score of 1.2 is less successful than 2.1, as better medals are worth more. We would also want to look at the total count of medals to see overall success and that could give us an idea of success per population, historical success in general, etc. These will all be necessary to help answer our hypothesis. 